\section{Computation of Kronecker's Canonical Form}
The following chapter deals with the problem of computing Kronecker's canonical form for a matrix pair \((A, B)\).
The approach described will be shown to be correct, and an
\href{https://github.com/liviusi/kronecker-canonical-form}{implementation}
of it using the CAS SageMath has been made publicly available under MIT License on GitHub.


We shall divide the procedure into two steps: the first one deals with regular pencils of matrices, the other with
singular pencils.

At the end of each of the following sections, the steps described shall be summarised in pseudocode.

\subsection*{Regular pencils.}
Throughout this section, we'll denote with \(P_{i}\) the matrix used for a similarity transformation.

Let \(\Gamma(\lambda) = A + \lambda B\) be a regular pencil of \(n \times n\) matrices.

We can find a number \(c\) such that
\[
    det(A + cB) \neq 0.
\]
We define \(A_{1} = A + cB\) and rewrite the pencil as
\[
    \Gamma(\lambda) = A_{1} + (\lambda - c)B.
\]
\(A_{1}\) being invertible for construction allows us to premultiply the pencil by \(A_{1}^{-1}\), and thus obtain
\[
    I + (\lambda - c)A_{1}^{-1} B.
\]
We compute the JCF of \(A^{-1}B\) and partition it into two blocks
\begin{gather*}
    P_{1}^{-1} (A_{1}^{-1} B) P_{1} = \{ J_{0}; J_{1} \}\\
    I + (\lambda - c)\{J_{0}; J_{1}\} = \{I - cJ_{0} + \lambda J_{0}; I - cJ_{1} + \lambda J_{1}\},
\end{gather*}
with \(J_{0}\) nilpotent Jordan matrix and \(det(J_{1}) \neq 0\).

Now, we can postmultiply the first diagonal block by \((I -cJ_{0})^{-1}\) and obtain
\[
    (I - cJ_{0} + \lambda J_{0}) (I - cJ_{0})^{-1} = I + \lambda(I - cJ_{0})^{-1} J_{0},
\]
which can be put in JCF as
\[
    P_{2}^{-1} ((I - cJ_{0})^{-1} J_{0}) P_{2} = \{N^{(u_{1})}; N^{(u_{2})}; ...; N^{(u_{s})}\},
\]
with \(N^{(u)} = I^{(u)} + \lambda H^{(u)}\), \(I^{(u)}\) the \(u \times u\) identity matrix and \(H^{(u)}\) the
\(u \times u\) upper shift matrix.

Lastly, we postmultiply the second diagonal block by \(J_{1}^{-1}\)
\[
    (I - cJ_{1} + \lambda J_{1}) J_{1}^{-1} = J_{1}^{-1} - cI + \lambda I
\]
and write the constant term in JCF
\[
    P_{3}^{-1} (J_{1}^{-1} - cI) P_{3} = J.
\]

To conclude, we shall present the aforementioned steps in pseudocode.
\begin{algorithm}
    \caption{Procedure to compute KCF of a regular pencil.}\label{alg:kcf-regular}
    \KwData{$\Gamma(\lambda) = A + \lambda B$: regular pencil}
    \KwResult{$K(\Gamma(\lambda))$: KCF of the pencil of matrices $\Gamma(\lambda)$}
    $c \gets -1$\;
    \While{True}{
        $c \gets $ random integer\;
        \eIf{$det(\Gamma(c)) = 0$}{
            \Continue
        }
        {
            $A_{1} \gets A + c*B$\;
            $J_{A_{1}} \gets $ jordan($A_{1}*B$)\;
            $\{J_{0}, J_{1}\} \gets$ submatrices($J_{A_{1}}$)\;
            $\{N_{i}\}_{i \geq 0} \gets $ jordan($(I - c*J_{0})^{-1} * J_{0}$)\;
            $J \gets $ jordan($J_{1}^{-1} - c*I$)\;
            $K(\Gamma(\lambda)) \gets $ diag($\{N_{i}\}, J +\lambda I$)
        }
    }
\end{algorithm}

We have now proved the following theorem.
\begin{theorem}[KCF of a regular pencil of matrices]
    Every regular pencil of matrices \(\Gamma(\lambda) = A + \lambda B\) can be reduced to a matrix of the form
    \[
        \begin{bmatrix}
            N^{(u_{1})} \\
            & N^{(u_{2})} \\
            & & \ddots \\
            & & & N^{(u_{s})} \\
            & & & & J + \lambda I
        \end{bmatrix},
    \]
    where the first \(s\) diagonal blocks correspond to infinite elementary divisors
    \(\mu^{u_{1}}, ..., \mu^{u_{s}}\) of \(\Gamma(\lambda)\) and the last block is uniquely determined by the
    finite elementary divisors of the given pencil.

    \(N^{(u)}\) is a \(u \times u\) square matrix such that
    \[
        \begin{bmatrix}
            1 & \lambda & & & \\
            0 & & \ddots & & \\
            & & & 1 & \lambda \\
            & & & & 1
        \end{bmatrix}
        = I^{(u)} + \lambda H^{(u)},
    \]
    with \(I^{(u)}\) a \(u \times u\) identity matrix and \(H^{(u)}\) \(u \times u\) upper shift matrix.
\end{theorem}

\subsection*{Singular pencils.}
\begin{theorem}[Reduction theorem]
    If the equation given by a matrix pair \(\Gamma(\lambda) = (A, B)\) has a solution of minimal
    degree \(\epsilon > 0\), then \(\Gamma(\lambda)\) is strictly equivalent to a pencil of matrices of the form
    \[
        \begin{bmatrix}
            L_{\epsilon} & 0 \\
            0 & \tilde{A} + \lambda \tilde{B}
        \end{bmatrix},
    \]
    where the equation analogous for \((\tilde(A), \tilde(B))\) has no solution of degree \(\alpha < \epsilon\) and
    \(L_{\epsilon}\) an \(\epsilon \times \epsilon + 1\) matrix such that
    \[
        \begin{bmatrix}
            \lambda & 1       & 0     & \hdots & 0       &    0   \\
            0       & \lambda & 1     &        & \vdots  & \vdots \\
            \vdots  & \vdots & \ddots & \ddots \\
            0       &        &        &        & \lambda & 1
        \end{bmatrix}.
    \]
\end{theorem}